Supplementary figures\nCapturing regeneration in models of forest dynamics

### 2022-12-14 manuscript/supplementaryRW.Rmd
add correc numbering of figures in the supplementary material

---
title: "Supplementary figures\nCapturing regeneration in models of forest dynamics"
author: 
- Olalla Díaz-Yáñez, 
- Yannek Käber, 
- Mats Mahnken, 
- Samuel Fischer, 
- Xavier Morin, 
- Manfred Lexer, 
- Christian Hochauer, 
- Katarina Merganicova, 
- Tobias Mette, 
- Werner Rammer, 
- Kristin H. Braziunas, 
- Paola Mairota, 
- Josef Bruna,
- Heike Lischke, 
- Daniel Scherrer, 
- Simon Scheiter, 
- Thomas Hickler, 
- Tim Anders,
- Jessica Hetzer, 
- Harald Bugmann
date: "`r Sys.Date()`"
output: 
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
    latex_engine: xelatex
    extra_dependencies: ["flafter", "float"]
    toc: yes
bibliography: Regeneration.bib
link-citations: yes
linkcolor: blue
csl: draft.csl
editor_options: 
  markdown: 
    wrap: 72
header-includes:
- \usepackage[left]{lineno}
- \linenumbers
---

@@

# Supplementary figures and tables

```{r mortTable, echo=FALSE,  message=FALSE}
library(knitr)

sigDiff <- readr::read_csv(here::here("figures", "mortRatio7_10.csv"))

kable(sigDiff,  format = "latex", caption = "Test of the significance of the differences of rate of recruitment at 7 cm threshold over 10 cm threshold.") |>
#kableExtra::landscape() 
kableExtra::kable_styling(full_width = F, latex_options = "scale_down")
```

# Model reports

## 4C

@@

• How have you defined the species composition in your model simulation?
(e.g., species levels, PFTs, etc.)? Please describe the species
categories used.

@@

• How have you defined the simulation area for your model (e.g., size
and other relevant site aspects)?

@@

• What are the relevant aspects of the dispersal (if any) and seed input
parameters in your model?

@@

• What is the simulation length, and how have you determined the
simulation time until the equilibrium?

@@

• If you have run more than one simulation per site, please describe the
differences of the approaches used.

@@

# Protocol

>>>>

---
title: "Supplementary figures\nCapturing regeneration in models of forest dynamics"
author: 
- Olalla Díaz-Yáñez, 
- Yannek Käber, 
- Mats Mahnken, 
- Samuel Fischer, 
- Xavier Morin, 
- Manfred Lexer, 
- Christian Hochauer, 
- Katarina Merganicova, 
- Tobias Mette, 
- Werner Rammer, 
- Kristin H. Braziunas, 
- Paola Mairota, 
- Josef Bruna,
- Heike Lischke, 
- Daniel Scherrer, 
- Simon Scheiter, 
- Thomas Hickler, 
- Tim Anders,
- Jessica Hetzer, 
- Harald Bugmann
date: "`r Sys.Date()`"
output: 
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
    latex_engine: xelatex
    extra_dependencies: ["flafter", "float"]
    toc: yes
bibliography: Regeneration.bib
link-citations: yes
linkcolor: blue
csl: draft.csl
editor_options: 
  markdown: 
    wrap: 72
header-includes:
- \usepackage[left]{lineno}
- \linenumbers
- \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}

---

@@

# Supplementary Material 1: Protocol

# Supplementary Material 2: Model reports

## 4C
### Authors

@@

@@

@@

@@

@@

@@

\newpage
\beginsupplement

#  Supplementary Material 3: Supplementary figures and tables

## Model complexity

Summary of the linear model of the overestimation proportions versus the mean complexity value on the establishment module.
```{r tableComp, echo=FALSE,  message=FALSE, render = 'normal_print'}
library(knitr)

tableCompOver <- readr::read_csv(here::here("figures", "tableCompOver.csv"))
jtools::summ(lm(overestimation ~ complexity, data = tableCompOver), model.info = FALSE, digits = 5)

```

```{r mortTable, echo=FALSE,  message=FALSE}
# library(knitr)
# 
# sigDiff <- readr::read_csv(here::here("figures", "mortRatio7_10.csv"))
# 
# kable(sigDiff,  format = "latex", caption = "Test of the significance of the differences of rate of recruitment at 7 cm threshold over 10 cm threshold.") |>
# #kableExtra::landscape() 
# kableExtra::kable_styling(full_width = F, latex_options = "scale_down")
```
